\begin{center}
    \LARGE
    \textbf{Acknowledgements}
    \vspace{0.5cm}
\end{center}

First and foremost, I would like to express my gratitude to Dr Daniel Rigden for his supervision throughout my PhD and previous projects. His experience and guidance was invaluable, and I strongly believe that I am going to benefit from what I have learned under his supervision in years to come. I would also like to thank him for his never-ending support and patience when computer programming seemed more important than research to me.

I would also like to thank my secondary supervisor Prof Olga Mayans. Six years ago, Olga gave me my first Bioinformatics research experience, and sparked an interest in computational work that lasts to this date. I would also like to thank her for her continued support and critical opinion throughout all of my projects.

Besides my supervisors, I would like to thank Dr Jens Thomas for his help throughout my PhD project. His patience was always appreciated when simple concepts proved difficult to grasp, and his critical mind and strive for simplicity also helped me to becoming a better researcher and Software Engineer, for which I am very grateful. I would also like to thank Dr Ronan Keegan, whose support was essential to understanding the mysterious and complex world of X-ray crystallography a little better. I would also like to thank all other members of the CCP4 and CCP-EM core teams for their help and support with all software related issues.

My thanks also go out to my funding bodies, the BBSRC and CCP4, without whose fincancial support this research could have not been conducted.

Last but not least I would like to thank Joanna Lorek, Peter, Petra, Viera and Peter \v{S}imkovic, and the rest of my family for their selfless support, help and patience whenever it was needed. All sacrificed significant parts of their lives to making my achievements possible, and thus this work is as much theirs as it is mine. My gratitude to all is beyond words.
